On the marginal value of swimming in woodland caribou

### 2021-04-12 paper/manuscript.Rmd
acknowledgements

**Acknowledgements**
We thank M. Laforge, M. Bonar, C. Hart, and R. Huang for help in the field.
Logistical support was provided by L. Bixby. We thank all members of the
Wildlife Evolutionary Ecology Lab, including C. Hart, C. Prokopenko, J. Kennah,
J.W. Turner, and S. Boyle for their comments on previous versions of this
manuscript. Newfoundland Wildlife Division including S. Moores, B. Adams, C.
Doucet, W. Barney, and J. Neville for logistical support in the field as well as
help with data data collection and management. We thank T. Bergerud and S.
Mahoney for their vision in initiating much of the work on caribou in
Newfoundland. Funding for this study was provided by the National Sciences and
Engineering Research Council (QMRW, JGH, EVW). We respectfully acknowledge the
territory in which data were collected and analyzed as the ancestral homelands
of the Beothuk, and the island of Newfoundland as the ancestral homelands of the
Mi’kmaq and Beothuk.

>>>>

**Acknowledgements**
We thank M. Laforge, M. Bonar, C. Hart, and R. Huang for help in the field. Logistical support was
provided by L. Bixby. We thank J. Schaefer and one anonymous reviewer as well as all members of the
Wildlife Evolutionary Ecology Lab for their comments on previous versions of this manuscript.
Newfoundland Wildlife Division including S. Moores, B. Adams, C. Doucet, W. Barney, and J. Neville for
logistical support in the field as well as help with data data collection and management. We thank T.
Bergerud and S. Mahoney for their vision in initiating much of the work on caribou in Newfoundland.
Funding for this study was provided by the Natural Sciences and Engineering Research Council (QMRW,
JGH, EVW). We respectfully acknowledge the territory in which data were collected and analyzed as the
ancestral homelands of the Beothuk, and the island of Newfoundland as the ancestral homelands of the
Mi’kmaq and Beothuk.
